---
title: "Logistic Regression Model in R"
author: "Sachin Sharma"
date: "12/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library (readr)
library(RCurl)
library(curl)
library(tidyverse)
library(ggplot2)

urlfile = "https://raw.githubusercontent.com/bkrai/R-files-from-YouTube/main/binary.csv"


mydata<-read_csv(url(urlfile))

head(mydata)

```


```{r}
str(mydata)
```

# Lets change admit and rank into categorical values 


```{r}
mydata$admit <- as.factor(mydata$admit)
mydata$rank <- as.factor(mydata$rank)

str(mydata)


```
# now we can see that both variables have changed to factor 

# now lets do partition of data set uring caTools 

```{r}

library(caTools)
set.seed(1234)

split <- sample.split(mydata$admit,SplitRatio = 0.8)

sample_train <- subset(mydata,split ==T)
sample_test <- subset(mydata,split==F)

head(sample_test)

```

# Lets create Logistic regression model 

```{r}

glm <- glm(admit~gre+gpa + rank, data = sample_train,
           family = "binomial")
summary(glm)

```
# Now lets run the code by removing gpa, as it is not statistically significant



```{r}

finalmodel <- glm(admit~gre+rank, data = sample_train,
           family = "binomial")
summary(finalmodel)


```

# Lets do some prediction 

```{r}

p1 <- predict(finalmodel,sample_train,type = "response")

head(p1)
```

```{r}
head(sample_train)
```

# Misclassification error - train data 

```{r}

pred1 <- ifelse(p1>0.5,1,0)

```


# Creating the confusion matrix 

```{r}
tab1 <- table(pred1,sample_train$admit)

# here 89+10 is missclassification error of our model in train data 

1-sum(diag(tab1))/sum(tab1)
```
## now checking the missclassification error in the test data : 

```{r}

p2 <- predict(finalmodel,sample_test, type = "response")





#tab2


pred2<- ifelse(p2>0.5,1,0)


tab2 <- table(pred2,sample_test$admit)
#tab2

```

## Missclassification error : 

```{r}
1-sum(diag(tab2))/sum(tab2)

```

# Goodness of fit : 

```{r}
with(finalmodel,pchisq(null.deviance-deviance, df.null-df.residual,lower.tail = F))
```

# Here we get this p values , which is very less = 0.000050, hence we can say our confidence level is high that this model is statistically significant...